### 2021-08-18 sections/healthcare_application/main.tex
Apply changes based on alex and proselint

The patients that are distributed by the EMS arrive at the hospital via an 
ambulance and are then either unloaded at the ED or remain blocked outside in 
the ambulance.
Whether or not the ambulance and the patient remain blocked is determined by 
the threshold that the given ED chooses to play.
High threshold indicates that the ED accepts patients even if it is relatively 
full, while low threshold means that the ED blocks ambulances more easily.

The game to be played now is between the two EDs and the EMS. 
The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system lie within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}).

@@

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for these particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a very short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) simply leaves 
less potential for improvement.

>>>>

The patients that are distributed by the EMS arrive at the hospital via an 
ambulance and are then either unloaded at the ED or stay blocked outside in 
the ambulance.
Whether or not the ambulance and the patient stay blocked is determined by 
the threshold that the given ED chooses to play.
High threshold indicates that the ED accepts patients even if it is relatively 
full, while low threshold means that the ED blocks ambulances more frequently.

The game to be played now is between the two EDs and the EMS. 
The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}).

@@

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for these particular set of parameters the strategies of 
the two hospitals converge over time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a short amount of time while 
hospital 1 takes longer and goes through numerous strategies to get there.

@@

By increasing \(\lambda_2\) there is no change as to how players behave
(\(T_1 = 5, T_2 = 6\)), but the efficiency of the system does change. 
There is a decline in the price of anarchy of the blocking time which at first 
glance indicates that upon flooding the system it becomes more efficient. 
This is non-sensical though.
What it really shows is that the steep increase in \( \lambda_2 \) leaves 
less potential for improvement.
